---
title: "QA/QC Fishing For Science Data"
author: "Camila Vargas"
date: "2/15/2022"
output: html_document
---

## Set-up
```{r setup, include=FALSE}

## Load packages
library(here)
library(tidyverse)
library(janitor)
library(lubridate)
library(freeR)

## Sets R not to use scientific notations
options(scipen=999) 

```

## Read Data
```{r}
daily_log_raw <- read_csv(here::here("6.raw_data/Daily_Log_FishingForScience.csv"))

tag_raw <- read_csv(here::here("6.raw_data/Tagging_data_FishingForScience.csv"))

```


## Exploring

1. Daily Logs
```{r}
str(daily_log_raw)
colnames(daily_log_raw)
complete(daily_log_raw)

sort(unique(daily_log_raw$TripID))
sort(unique(daily_log_raw$Date))
sort(unique(daily_log_raw$Area))
sort(unique(daily_log_raw$`Envirmomental Conditions`))
sort(unique(daily_log_raw$Guide))
sort(unique(daily_log_raw$`Gear Type`))
sort(unique(daily_log_raw$`Movement  Mode`))
sort(unique(daily_log_raw$`Primary Target`))
sort(unique(daily_log_raw$Notes))
```

- Column `Date` is class character. Format "mm/dd/yyyy"
- Column 13 to 36 are species name. Format = common name (scientific name)
- Column `Longnose Emperor (Lethrinus olivaceus)` has 1 NA
- Column `Area` has values for Zone 2 and Zone_2, are these the same? Same for Zone, 3,4,5, and 6.
- Do we need coordinates for column `Area`?
- Should `Environmental Conditions` be harmonized?


2. Tags

```{r}
str(tag_raw)

sort(unique(tag_raw$TripID))
sort(unique(tag_raw$Date))
sort(unique(tag_raw$Area))
sort(unique(tag_raw$Guide))
sort(unique(tag_raw$Angler))
sort(unique(tag_raw$`Species Code`))
sort(unique(tag_raw$`Species Name`))
sort(unique(tag_raw$Targeted))
sort(unique(tag_raw$Tagged))
sort(unique(tag_raw$`Fork Length (cm)`))
sort(unique(tag_raw$`Total Length (cm)`))
sort(unique(tag_raw$`Tag ID (5 character)`))
sort(unique(tag_raw$ReCap))
sort(unique(tag_raw$`Release Condition`))
sort(unique(tag_raw$`Gear Type`))
sort(unique(tag_raw$`GPS#`))
sort(unique(tag_raw$`Movement Method`))
sort(unique(tag_raw$PrimaryTarget))
sort(unique(tag_raw$Notes))

```


- Change column date to class date, format "mm/dd/yyyy" use `date = mdy(date)`?
- Area: Fix "Downeast" = "Down East", "Keyhole" = "Key Hole", "Smitty's" = "Smittys".
- Area: is West lagoon the same than Western Lagoon?
- Angler: Are Alana and Alena different person?
- Species Name: miss spelled "Cephlapholus argus" = "Cephalopholis argus".
- Species Name: Which one is correct? "Lutjanus fuluvus" or "Lutjanus fulvus"
- Species Name: Which one is correct? "Lutjanus monostigma" or "Lutjanus monstigma"
- Species Name: Which one is correct? "Scomberiodes lysan" or "Scomberoides lysan"
- Fork Length and Total Length: change "NO DATA" to NA
- tag ID 5 characters: Is "EFA##" correct?, remove space from ""EFA 21"?, change "NO DATA" to NA
- ReCap: Change "NO DATA" to NA
- Clean colnames


--------------------------------------------
Areas in Daily Log that are not in tag therefore there is no coords
"Frigate Flat"
"North Forreef"
"South Forreef"







